Propositions as Sessions, Mechanically

### 2015-04-27 paper/presentation.tex
Working on GV/Translation parts of talk now.
Almost there.

\begin{frame}
\oldframetitle{Preliminaries}
\begin{itemize}
\item Locally Nameless
  \begin{itemize}
  \item Avoids variable capture
  \item de Bruijn indices for bound variables
    ($\lambda~(\lambda~1) \equiv \lambda x. \lambda y. x$)
  \end{itemize}
\item Cofinite Quantification
  \begin{itemize}
  \item stronger induction principle
  \item
    \begin{math}
    \begin{array}{lcl}
      \mbox{Exists-Fresh} & & \mbox{Cofinite}\\
      \inference{
        x \notin FV(N) &
        \Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U}
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    & \mbox{vs}. &
      \inference{
        \forall x \notin L.
        (\Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U})
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    \end{array}
    \end{math}
  \end{itemize}
\item Metatheory library for representation
\end{itemize}
\note{
one of the key issues when formalising programming language metatheory is how
to represent variables both bound and free. I chose the locally nameless
representation which separates bound and free variables into distinct
entities. Thus it avoids the variable capture problem in contrast to other
approaches.

@@

\begin{frame}
GV is similar
\note{

@@

\begin{frame}
something about a translation

\note{

the translation to CP is
presented. blah blah something about the session types being a little odd or
overlook this probably

the translation seems to require a duplication of the specifications for cp
and gv typing rules not done

>>>>

\begin{frame}
\ftitle{Preliminaries}{2}
\begin{itemize}
\item Locally Nameless
  \begin{itemize}
  \item Avoids variable capture
  \item de Bruijn indices for bound variables
    ($\lambda~(\lambda~1) \equiv \lambda x. \lambda y. x$)
  \end{itemize}
\item Cofinite Quantification
  \begin{itemize}
  \item stronger induction principle
  \item
    \begin{math}
    \begin{array}{lcl}
      \mbox{Exists-Fresh} & & \mbox{Cofinite}\\
      \inference{
        x \notin FV(N) &
        \Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U}
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    & \mbox{vs}. &
      \inference{
        \forall x \notin L.
        (\Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U})
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    \end{array}
    \end{math}
  \end{itemize}
\item Metatheory library for representation
\end{itemize}
\note{
one of the key issues when formalising programming language metatheory is how
to represent variables both bound and free. I chose the locally nameless
representation which separates bound and free variables into distinct
entities. Thus it avoids the variable capture problem in contrast to other
approaches.

@@

\begin{frame}[fragile]
\ftitle{GV}{2.5}
\begin{itemize}
\item GV similar to CP (types, terms, well-typed relation, $\ldots$)
\item Representation choices (Kindedness, Sessions)
\end{itemize}
\begin{coqp}
Inductive wf_typ : typ -> kind -> Prop :=
  | $\ldots$
  | wf_labs : forall kt ku T U
                     (WFT: wf_typ T kt)
                     (WFU: wf_typ U ku),
                wf_typ (T $\lolli$ U) lin
  | $\ldots$
\end{coqp}
\note{

@@

\begin{frame}[fragile]
\ftitle{Translation from GV to CP : Work in Progress}{1}
\begin{theorem}[Translation]
If a GV term is well-typed then its translation is well-typed in CP.
\end{theorem}
Issues
\begin{itemize}
\item type inference, positive cases and duplication
\end{itemize}
\begin{coqp}
trans_case:
  forall L $S_1$ $S_2$ M NL NR P QL QR G H z
         (INFM: inferTy M G ($S_1$ $\with$ $S_2$))
         (TR: transTm M G 0 P)
         (TRNL: forall x (NIN: x $\notin$ L),
                  transTm (open NL x) (x $\sim$ $S_1$ ++ H) z QL)
         (TRNR: forall x (NIN: x $\notin$ L),
                  transTm (open NR x) (x $\sim$ $S_2$ ++ H) z QR),
  transTm (tm_case M NL NR) (G++H) z
          ($\nu \sem{S_1 \with S_2}$t.(P $\mid$ 0 CASE QL OR QR))
\end{coqp}
\note{

continuation-passing style.

A well-typed term in GV is parameterised by a name representing the channel
which communicates the result of its translation
